The Expected Place of the Local Group in the Cosmic Web

### 2014-08-12 paper/main.tex
updated the prefered environment

The LG analogues or General Sample (GS) in this paper are pairs selected in
relative isolation, and in a wide range of masses from  $M_{200c}=5
\times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
Isolation criteria includes a pair closer than $1.3$\mpc, and with no
massive neighbors within $5$\mpc.
In addition we require that pairs have no Virgo-like neighbor halo
with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
Mpc.  
We have $5480$ pairs under these general criteria. 
A full description of the selection criteria can be found in
\citet{lganalogues,sat}.

We also define two subsamples more closely related to the MW-M31 
dynamics according to the tolerance in additional constraints.
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. 
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues} results, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlaps, also we removed a couple pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

The first result we explore is the kind of environment occupied by
our LGs. 
We find that the LGs in the general sample are located across
all different evironment without any strong preferences; $1/3$  are
located in sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning
$1/6$ in voids.

The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
different. 
By large the LGs in these samples are located in filaments and sheets. 
In both samples, $\sim 50\%$ of the pairs can be found in filaments
while $\sim 40\%$ are in sheets. 
These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

This difference between the general and the restricted samples is
due the mass ranges covered by each sample. 
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
is very narrow and it is used to constraint the LG mass.
We show  in table \ref{table:web_type} that subset of the GS
having a similar mass range to $2\sigma$ and $3\sigma$ reproduces  
similar environment fractions.

Figure \ref{fig:median_fraction} clearly shows the correlation between
environment an total pair mass.
Each line represents the mass distribution of pairs in the four
different environments for the general sample.
High mass pairs tend to be located in  peaks and filaments while less
massive ones in voids and sheets. 
The shaded regions represent the $68\%$ confidence intervals of the mass 
distributions of $2\sigma$ and $3\sigma$ samples.

>>>>

The LG analogues or General Sample (GS) in this paper are pairs selected in
relative isolation, and in a wide range of masses from  $M_{200c}=5
\times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
Isolation criteria includes no halos more masive than each member in
the pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
In addition we require that pairs have no Virgo-like neighbor halo
with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
Mpc.  
We have $5480$ pairs under these general criteria. 
A full description of the selection criteria can be found in
\citet{lganalogues,sat}.

We also define two subsets of restricted samples (RS) more closely
related to the MW-M31  dynamics according to the tolerance in
additional constraints. 
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly.  
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues} results, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlaps, also we removed a couple pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

The first result we explore is the kind of environment occupied by
our LGs. 
We find that the LGs in the GS are located across all different
evironment without any strong preferences; $1/3$  are located in
sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
voids.

The situation in the $2\sigma$ and $3\sigma$ samples is very
different. 
By large the LGs in these samples are located in filaments and sheets. 
In both samples, $\sim 50\%$ of the pairs can be found in filaments
while $\sim 40\%$ are in sheets. 
These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

We find that the difference between the GS and the RS 
can be explained by the total pair mass.
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
amples is very narrow and it is used to constraint the LG mass.
We show in Table \ref{table:web_type} that a subset of the GS
having a similar mass range than the RS reproduces similar environment
fractions.

Figure \ref{fig:median_fraction} summarizes this correlation between
environment an total pair mass.
Each line represents the mass distribution of pairs in the four
different environments for the GS.
High mass pairs tend to be located in  peaks and filaments while less
massive ones in voids and sheets. 
The shaded regions represent the $68\%$ confidence intervals of the mass 
distributions of $2\sigma$ and $3\sigma$ samples.
